---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# transfer

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/kvasilopoulos/transfer.svg?branch=master)](https://travis-ci.org/kvasilopoulos/transfer)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kvasilopoulos/transfer?branch=master&svg=true)](https://ci.appveyor.com/project/kvasilopoulos/transfer)
<!-- badges: end -->

The goal of {transfer} is to utilize the power of [transfer.sh](https://transfer.sh) through R. \code{transfer.sh} is a website and not a script, which helps users to share files from the command-line an efficient way. It won’t required any additional software to work except pre-installed application such as curl. 

## Install

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kvasilopoulos/transfer")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r load}
library(transfer)
```

## Create Files and Directories to use in my examples

```{r create, echo=TRUE, message=FALSE, warning=FALSE}
file.create("file.txt")
dir.create("folder")
file.create("zipfile.zip")

```

## File

```{r file}
tf_upload("file.txt")
```

## Folder

```{r folder}
tf_upload("folder")
```

## Zip

```{r zip}
tf_upload("zipfile.zip")
```

```{r remove, include=FALSE}
unlink("file.txt")
unlink("folder", recursive=TRUE)
unlink("zipfile.zip")

```

## TODO 

Currently {transfer} works only for the files/folders located in the working directory.
Still needs some path manipulation to be done.
