---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# transfersh

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/kvasilopoulos/transfersh/workflows/R-CMD-check/badge.svg)](https://github.com/kvasilopoulos/transfersh/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/transfersh)](https://CRAN.R-project.org/package=transfersh)
<!-- badges: end -->

The goal of {transfersh} is to utilize the power of [transfer.sh](https://transfer.sh) through R. \code{transfer.sh} is a website and not a script, which helps users to share files from the command-line an efficient way. It won’t required any additional software to work except pre-installed application such as curl. 

## Install

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kvasilopoulos/transfer")
```

## Example

This is a basic example which shows you how to use {transfersh}:

```{r load}
library(transfersh)
```

To upload a file you can easily use the name of the file and the path where the file is located, if it is not in the working directory. In case  of a folder or multiple files `tf_upload` will bundle all contents and zip it  into a single file. Then it will upload the zip and delete the zip that was created locally.

## File

```{r file}
tf_upload("file.txt", path = "inst/examples")
```

## Folder

```{r folder}
tf_upload("folder", path = "inst/examples")
```

